
\begin{abstract}%    
Linear Fisher markets are a fundamental economic model with applications in Internet advertising and fair division. 
In the finite-dimensional case of $n$ buyers and $m$ items, a market equilibrium can be computed using the Eisenberg-Gale convex program. 
  Motivated by large-scale applications, this paper considers a generalization of a linear Fisher market where there is a finite set of buyers and a continuum of items.
  We introduce generalizations of the Eisenberg-Gale convex program and its dual to this infinite-dimensional setting, which leads to Banach-space optimization problems.
  We establish existence of optimal solutions, strong duality, as well as necessity and sufficiency of KKT-type conditions, via non-standard arguments which circumvent the limitations of duality theory in infinite-dimensional optimization.
  Furthermore, we show that there exists a pure equilibrium allocation, i.e., a division of the item space.
  When the item space is a closed interval and buyers have piecewise linear valuations, we show that the Eisenberg-Gale-type convex program over the infinite-dimensional allocations can be reformulated as a finite-dimensional convex conic program, which can be solved efficiently using off-the-shelf optimization software based on primal-dual interior-point methods. 
  Based on our convex conic reformulation, we develop the first polynomial-time cake-cutting algorithm that achieves Pareto optimality, envy-freeness, and proportionality.
%   For general buyer valuations or a very large number of buyers, we propose computing market equilibrium using stochastic dual averaging, which finds approximate equilibrium prices with high probability. 
%   Finally, we discuss how the above results easily extend to the case of quasilinear utilities.

\smallskip
\noindent \textbf{Keywords.} Fisher markets, equilibrium computation, fair division, convex optimization.
\end{abstract}%
